---
title: "Final project---RNA-seq analysis with limma"
output: html_notebook
---

1 Set-up
```{r}
library(limma)
library(Glimma)
library(edgeR)
library(Homo.sapiens)
```

2 Dta packaging
# Combined into a matrix of counts using the readDGE function
# Phenotype (disease status)/"lung cancer or nomral tissue" be associated with the columns of the counts matrix
```{r}
files <- c("lungcancer1.txt", "lungcancer2.txt", "lungcancer3.txt", "lungcancer4.txt", "lungcancer5.txt","lungcancer6.txt", "lungcancer7.txt", "lungcancer8.txt", "lungcancer9.txt", "lungcancer10.txt", "lungcancer11.txt", "lungcancer12.txt", "lungcancer13.txt", "lungcancer14.txt", "lungcancer15.txt", "lungcancer16.txt", "lungcancer17.txt", "lungcancer18.txt", "lungcancer19.txt", "lungcancer20.txt", "lungcancer21.txt", "lungcancer22.txt", "lungcancer23.txt", "lungcancer24.txt", "lungcancer25.txt", "lungcancer26.txt", "lungcancer27.txt", "lungcancer28.txt", "lungcancer29.txt", "lungcancer30.txt", "normal1.txt", "normal2.txt", "normal3.txt", "normal4.txt", "normal5.txt", "normal6.txt", "normal7.txt", "normal8.txt", "normal9.txt", "normal10.txt", "normal11.txt", "normal12.txt", "normal13.txt", "normal14.txt", "normal15.txt", "normal16.txt", "normal17.txt", "normal18.txt", "normal19.txt", "normal20.txt", "normal21.txt", "normal22.txt", "normal23.txt", "normal24.txt", "normal25.txt", "normal26.txt", "normal27.txt", "normal28.txt", "normal29.txt", "normal30.txt")
read.delim(files[1], header=FALSE, nrow=5)
x <- readDGE(files)
class(x)
dim(x)
group <- as.factor(rep(c("lungcancer", "normal"), c(30, 30)))
x$samples$group <- group
x$samples
```
# Organising gene annotations
# Retrieve a second data frame named genes in the DGEList-object to store gene-level information associated with rows of the counts matrix using Homo.sapiens package.
```{r}
geneid <- rownames(x)
genes <- select(Homo.sapiens, keys=geneid, columns=c("SYMBOL", "TXCHROM"), 
                keytype="ENSEMBL")
head(genes)
genes <- genes[!duplicated(genes$ENSEMBL),]
x$genes <- genes
x
```


